### 2020-09-07 README.Rmd
transfer of links to open-AIMS

```{r, echo = FALSE}
version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])
version <- gsub('-', '.', version)
```

@@

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/dataaimsr/actions)
![pkgdown](https://github.com/AIMS/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
<!-- badges: end -->

@@

`dataaimsr` is the **AIMS Data Platform R Client**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://aims.github.io/data-platform).

@@

**AIMS Data Platform** requires an API Key for requests, [get a key here.](https://aims.github.io/data-platform/key-request)

The API Key can be passed to the package functions as an additional `api_key = 'XXXX'` argument, however it is preferred that API Keys are not stored permanently in your machine.

@@

```{r, eval = FALSE}
devtools::install_github("https://github.com/AIMS/dataaimsr")
```

@@

The **AIMS Data Platform API** is a *REST API* providing *JSON* formatted data. Documentation about available data sets can be found on the [AIMS Data Platform API](https://aims.github.io/data-platform).

@@

Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://aims.github.io/dataaimsr).

>>>>

```{r, echo = FALSE}
version <- as.vector(read.dcf("DESCRIPTION")[, "Version"])
version <- gsub("-", ".", version)
```

@@

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/open-AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/open-AIMS/dataaimsr/actions)
![pkgdown](https://github.com/open-AIMS/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
[![Ask Us Anything
\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/open-AIMS/dataaimsr/issues/new)
![Open Source
Love](https://badges.frapsoft.com/os/v2/open-source.svg?v=103)
<!-- badges: end -->

@@

`dataaimsr` is the **AIMS Data Platform R Client**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://open-aims.github.io/data-platform).

@@

**AIMS Data Platform** requires an API Key for requests, [get a key here.](https://open-aims.github.io/data-platform/key-request)

The API Key can be passed to the package functions as an additional `api_key = "XXXX"` argument, however it is preferred that API Keys are not stored permanently in your machine.

@@

```{r, eval = FALSE}
devtools::install_github("https://github.com/open-AIMS/dataaimsr")
```

@@

The **AIMS Data Platform API** is a *REST API* providing *JSON* formatted data. Documentation about available data sets can be found on the [AIMS Data Platform API](https://open-aims.github.io/data-platform).

@@

Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://open-aims.github.io/dataaimsr).
